---
title: "Human Development Index and Gross National Income relation in Brazil"
author: "Expedito Pinto de Paula Junior"
date: "11/18/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

The objective of this presentation is plot HDI (Human Development Index) Education Index and HDI GNI (Gross National Income) Index in all cities in Brazil. 

## HDI Education Index VS HDI GNI Index in all cities in Brazil

```{r plot1, message=FALSE, warning=FALSE}
library(plotly)
library(ggplot2)
brcities <- read.csv("BRAZIL_CITIES.csv", header = TRUE, sep = ";")
fig <- plot_ly(brcities,x=~IDHM_Educacao, y=~IDHM_Renda, type = "scatter", color = ~STATE, mode = "markers", marker = list(opacity = 0.7) ,text = ~paste("City:", CITY))
fig
```

## HDI Education Index VS HDI GNI Index in all cities in Brazil

```{r plot2, message=FALSE, warning=FALSE}

fig2 <- plot_ly(brcities,x=~IDHM_Educacao, y=~IDHM_Renda, type = "scatter", color = ~CAPITAL, mode = "markers", marker = list(opacity = 0.5), text = ~paste("City:", CITY))
fig2


```


## Some Findings

### The 5 best cities in relation btw HDI and GNI are: 
     1. São Caetano do Sul
     2. Niterói
     3. Vitoria
     4. Florianópolis
     5. Santos

### The 5 Best Capitals in relation btm HDI and GNI are:
     1. Vitória
     2. Florianópolis
     3. Brasilia
     4. Curitiba
     5. Belo Horizonte



